---
name: Julie D.
surname: White
position: "IRTA Postdoctoral Research Fellow"
address: "National Institute of Environmental Health Sciences"
email: "julie.white@nih.gov"
aboutme: "Trying to make things work"
github: juliedwhite
linkedin: julie-d-white
headcolor: 02818A
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=multiple-bibliographies.lua"] # used for creating bibliographies for multiple sections
    keep_tex: yes
csl: apa-cv.csl # change this if you want to use other citation styles
bibliography_published: "Published_Reviewed.bib" # use separate .bib files and assign each of them a unique key: bibliography_*
bibliography_inprogress: "In_progress.bib"
bibliography_nonreviewed: "Published_NonReviewed.bib" 
bibliography_presentations: "Presentations.bib"
nocite: '@*' # don't change this if you want to print out all the refs

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble); library(glue)
```

# Research Interests

* Genetic and environmental contributors to human phenotypic variation and health
* Epigenetic modifications in response to environmental exposures
* Gene x environment interactions
* Bioinformatics, statistical genetics, and data visualization 

# Education

```{r}
tribble(~ Degree, ~ Years, ~ Institution, 
        "B.S. in Genetics", "2010-2014", "Clemson University", 
        "M.A. in Anthropology", "2014-2016", "Penn State University", 
        "Ph.D. in Anthropology", "2016-2019", "Penn State University") %>%
  detailed_entries(with = Degree, what = Institution, where = Years)
```

# History
```{r}
tribble(~ Title, ~ When, ~ Institution, 
        "IRTA Postdoctoral Fellow", "2020-current", 
        "Epidemiology Branch; National Institute of Environmental Health Sciences", 
        "Instructor", "2019", "Penn State University", 
        "Graduate Research Assistant", "2014-2019", "Penn State University", 
        "Teaching Assistant", "2014-2018", "Penn State University", 
        "NSF REU Biochemistry Intern", "2013", "Texas A&M University", 
        "Summer Research Intern", "2012", "Greenwood Genetics Center", 
        "Undergraduate Researcher in Genetics and Biochemistry", "2010-2014", "Clemson University") %>%
  detailed_entries(with = Title, where = When, what = Institution)
```

# Computational Languages

# Publications

## In-progress

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_inprogress}
:::

\endgroup

## Peer-reviewed
<!-- Notes: copy and paste the following block for any other bibliography sections with the same bibliography key matched that you assigned in YAML  -->
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_published}
:::

\endgroup
<!-- Bib-printing block ends here. -->

## Non peer-reviewed

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_nonreviewed}
:::

\endgroup

# Grants and Awards

```{r}
tribble(~Year, ~Name,
        "2019", "National Science Foundation DDRIG ($31,535; awarded but declined)",
        "2017-2018", "PSU Hill Fellowship Award ($1500 and $1200)",
        "2017", "UW Summer Institutes in Statistical Genetics Travel Award ($1800)",
        "2016-2018", "PSU RGSO Conference Travel Award ($400 each year)",
        "2015", "PSU Center for Human Evolution and Diversity Research Grant ($7303") %>% 
  detailed_entries(where = Year, what = Name) 
```

# Invited Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {}
:::

\endgroup

# Conference Participation

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {}
:::

\endgroup

# Pedagogical Experience

## Student Advising

## Primary Instructor

## Graduate Student Instructor

# Professional Development

# University and Professional Service

## Ad Hoc Reviewer

* PLoS Genetics (1)
* Scientific Reports (1)

# Professional Memberships