%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{02818A}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Julie D.}{White}

\position{IRTA Postdoctoral Research Fellow}
\address{National Institute of Environmental Health Sciences}

\email{\href{mailto:julie.white@nih.gov}{\nolinkurl{julie.white@nih.gov}}}
\github{juliedwhite}
\linkedin{julie-d-white}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{Trying to make things work}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {May 2021}
    {Julie D. White~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{research-interests}{%
\section{Research Interests}\label{research-interests}}

\begin{itemize}
\tightlist
\item
  Genetic and environmental contributors to human phenotypic variation
  and health
\item
  Epigenetic modifications in response to environmental exposures
\item
  Gene x environment interactions
\item
  Bioinformatics, statistical genetics, and data visualization
\end{itemize}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Clemson University}{B.S. in Genetics}{2010-2014}{}{}\vspace{-4.0mm}
    \cventry{Penn State University}{M.A. in Anthropology}{2014-2016}{}{}\vspace{-4.0mm}
    \cventry{Penn State University}{Ph.D. in Anthropology}{2016-2019}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{history}{%
\section{History}\label{history}}

\begin{cventries}
    \cventry{Epidemiology Branch; National Institute of Environmental Health Sciences}{IRTA Postdoctoral Fellow}{2020-current}{}{}\vspace{-4.0mm}
    \cventry{Penn State University}{Instructor}{2019}{}{}\vspace{-4.0mm}
    \cventry{Penn State University}{Graduate Research Assistant}{2014-2019}{}{}\vspace{-4.0mm}
    \cventry{Penn State University}{Teaching Assistant}{2014-2018}{}{}\vspace{-4.0mm}
    \cventry{Texas A\&M University}{NSF REU Biochemistry Intern}{2013}{}{}\vspace{-4.0mm}
    \cventry{Greenwood Genetics Center}{Summer Research Intern}{2012}{}{}\vspace{-4.0mm}
    \cventry{Clemson University}{Undergraduate Researcher in Genetics and Biochemistry}{2010-2014}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{computational-languages}{%
\section{Computational Languages}\label{computational-languages}}

\begin{cventries}
    \cventry{}{R}{}{Advanced}{}\vspace{-4.0mm}
    \cventry{}{Bash}{}{Intermediate}{}\vspace{-4.0mm}
    \cventry{}{Python}{}{Intermediate}{}\vspace{-4.0mm}
    \cventry{}{Bioconductor}{}{Novice}{}\vspace{-4.0mm}
    \cventry{}{MATLAB}{}{Novice}{}\vspace{-4.0mm}
    \cventry{}{LaTeX}{}{Intermediate}{}\vspace{-4.0mm}
    \cventry{}{plink}{}{Advanced}{}\vspace{-4.0mm}
    \cventry{}{vcf- and bcftools}{}{Advanced}{}\vspace{-4.0mm}
    \cventry{}{shapeit}{}{Advanced}{}\vspace{-4.0mm}
    \cventry{}{Impute}{}{Advanced}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{in-progress}{%
\subsection{In-progress}\label{in-progress}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_inprogress}{}
\leavevmode\hypertarget{ref-Thanh_PesticideEWAS}{}%
Hoang, T. T., Qi, C., Paul, K. C., Lee, Mi Kyeong, \textbf{White, Julie
D.}, Richards, M., Auerbach, S. S., Long, S., Shrestha, S., Wang, T.,
Beane-Freeman, L. E., Parks, C., Consortium, B., Xu, C.-j., Ritz, B.,
Koppelman, G. H., \& London, S. J. (in review-). \emph{Epigenome-wide
dna methylation and pesticide use in the agricultural lung health
study}.

\endgroup

\hypertarget{peer-reviewed}{%
\subsection{Peer-reviewed}\label{peer-reviewed}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_published}{}
\leavevmode\hypertarget{ref-Hoskens_2021_BiometricMatching}{}%
Hoskens, H., Liu, D., Naqvi, S., Lee, M. K., Eller, R. J., Indencleef,
K., \textbf{White, Julie D.}, Li, J., Larmuseau, M. H. D., Hens, G.,
Wysocka, J., Walsh, S., Richmond, S., Shriver, M. D., Shaffer, J. R.,
Peeters, H., Weinberg, S. M., \& Claes, P. (2021). 3D facial phenotyping
by biometric sibling matching used in contemporary genomic methodologies
{[}Journal Article{]}. \emph{PLOS Genetics}, \emph{17}(5), 1--28.
\url{https://doi.org/10.1371/journal.pgen.1009528}

\leavevmode\hypertarget{ref-Indencleef_2021_NSCLP}{}%
Indencleef, K., Hoskens, H., Lee, M. K., \textbf{White, Julie D.}, Liu,
C., Eller, R. J., Naqvi, S., Wehby, G. L., Moreno Uribe, L. M., Hecht,
J. T., Long, R. E., Christensen, K., Deleyiannis, F. W., Walsh, S.,
Shriver, M. D., Richmond, S., Wysocka, J., Peeters, H., Shaffer, J. R.,
\ldots{} Claes, P. (2021). The intersection of the genetic architectures
of orofacial clefts and normal facial variation {[}Journal Article{]}.
\emph{Frontiers in Genetics}, \emph{12}(170).
\url{https://doi.org/10.3389/fgene.2021.626403}

\leavevmode\hypertarget{ref-White_Indencleef_2021_MetaGWAS}{}%
\textbf{White, Julie D.}, Indencleef, K., Naqvi, S., Eller, R. J.,
Hoskens, H., Roosenboom, J., Lee, M. K., Li, J., Mohammed, J., Richmond,
S., Quillen, E. E., Norton, H. L., Feingold, E., Swigut, T., Marazita,
M. L., Peeters, H., Hens, G., Shaffer, J. R., Wysocka, J., \ldots{}
Claes, P. (2021). Insights into the genetic architecture of the human
face {[}Journal Article{]}. \emph{Nature Genetics}, \emph{53}(1),
45--53. \url{https://doi.org/10.1038/s41588-020-00741-7}

\leavevmode\hypertarget{ref-Ekrami_2020_MultivariateAsymmetry}{}%
Ekrami, O., Claes, P., \textbf{White, Julie D.}, Weinberg, S. M.,
Marazita, M. L., Walsh, S., Shriver, M. D., \& Van Dongen, S. (2020). A
multivariate approach to determine the dimensionality of human facial
asymmetry {[}Journal Article{]}. \emph{Symmetry}, \emph{12}(3), 348.
\url{https://doi.org/10.3390/sym12030348}

\leavevmode\hypertarget{ref-Li_2020_AncestryInference}{}%
Li, J., Zarzar, T. G., \textbf{White, Julie D.}, Indencleef, K.,
Hoskens, H., Matthews, H., Nauwelaers, N., Zaidi, A., Eller, R. J.,
Herrick, N., Günther, T., Svensson, E. M., Jakobsson, M., Walsh, S., Van
Steen, K., Shriver, M. D., \& Claes, P. (2020). Robust genome-wide
ancestry inference for heterogeneous datasets: Illustrated using the
1,000 genome project with 3D facial images {[}Journal Article{]}.
\emph{Scientific Reports}, \emph{10}(1), 11850.
\url{https://doi.org/10.1038/s41598-020-68259-w}

\leavevmode\hypertarget{ref-White_2020_CameraVariation}{}%
\textbf{White, Julie D.}, Ortega-Castrillon, A., Virgo, C., Indencleef,
K., Hoskens, H., Shriver, M. D., \& Claes, P. (2020). Sources of
variation in the 3dMDface and vectra h1 3D facial imaging systems
{[}Journal Article{]}. \emph{Scientific Reports}, \emph{10}(1), 4443.
\url{https://doi.org/10.1038/s41598-020-61333-3}

\leavevmode\hypertarget{ref-Sero_2019_FaceToDNA}{}%
Sero, D., Zaidi, A., Li, J., \textbf{White, Julie D.}, Zarzar, T. B. G.,
Marazita, M. L., Weinberg, S. M., Suetens, P., Vandermeulen, D., Wagner,
J. K., Shriver, M. D., \& Claes, P. (2019). Facial recognition from dna
using face-to-dna classifiers {[}Journal Article{]}. \emph{Nature
Communications}, \emph{10}(1), 2557.
\url{https://doi.org/10.1038/s41467-019-10617-y}

\leavevmode\hypertarget{ref-White_2019_MeshMonk}{}%
\textbf{White, Julie D.}, Ortega-Castrillón, A., Matthews, H., Zaidi, A.
A., Ekrami, O., Snyders, J., Fan, Y., Penington, T., Van Dongen, S.,
Shriver, M. D., \& Claes, P. (2019). MeshMonk: Open-source large-scale
intensive 3D phenotyping {[}Journal Article{]}. \emph{Scientific
Reports}, \emph{9}(1), 6085.
\url{https://doi.org/10.1038/s41598-019-42533-y}

\leavevmode\hypertarget{ref-Zaidi_White_2019_Masculinity}{}%
Zaidi, A. A., \textbf{White, Julie D.}, Mattern, B. C., Liebowitz, C.
R., Puts, D. A., Claes, P., \& Shriver, M. D. (2019). Facial masculinity
does not appear to be a condition-dependent male ornament and does not
reflect mhc heterozygosity in humans {[}Journal Article{]}.
\emph{Proceedings of the National Academy of Sciences}, \emph{116}(5),
1633--1638. \url{https://doi.org/10.1073/pnas.1808659116}

\leavevmode\hypertarget{ref-Claes_2018_GlobalToLocal}{}%
Claes, P., Roosenboom, J., \textbf{White, Julie D.}, Swigut, T., Sero,
D., Li, J., Lee, M. K., Zaidi, A., Mattern, B. C., Liebowitz, C.,
Pearson, L., González, T., Leslie, E. J., Carlson, J. C., Orlova, E.,
Suetens, P., Vandermeulen, D., Feingold, E., Marazita, M. L., \ldots{}
Weinberg, S. M. (2018). Genome-wide mapping of global-to-local genetic
effects on human facial shape {[}Journal Article{]}. \emph{Nature
Genetics}, \emph{50}(3), 414--423.
\url{https://doi.org/10.1038/s41588-018-0057-4}

\leavevmode\hypertarget{ref-Ekrami_2018_MeasuringAsymmetry}{}%
Ekrami, O., Claes, P., \textbf{White, Julie D.}, Zaidi, A. A., Shriver,
M. D., \& Van Dongen, S. (2018). Measuring asymmetry from high-density
3D surface scans: An application to human faces {[}Journal Article{]}.
\emph{PloS One}, \emph{13}(12), e0207895--e0207895.
\url{https://doi.org/10.1371/journal.pone.0207895}

\leavevmode\hypertarget{ref-Indencleef_2018_SixNSCLP}{}%
Indencleef, K., Roosenboom, J., Hoskens, H., \textbf{White, Julie D.},
Shriver, M. D., Richmond, S., Peeters, H., Feingold, E., Marazita, M.
L., Shaffer, J. R., Weinberg, S. M., Hens, G., \& Claes, P. (2018). Six
nscl/p loci show associations with normal-range craniofacial variation
{[}Journal Article{]}. \emph{Frontiers in Genetics}, \emph{9}(502).
\url{https://doi.org/10.3389/fgene.2018.00502}

\leavevmode\hypertarget{ref-Rosenboom_2018_Testosterone}{}%
Roosenboom, J., Indencleef, K., Lee, M. K., Hoskens, H., \textbf{White,
Julie D.}, Liu, D., Hecht, J. T., Wehby, G. L., Moreno, L. M.,
Hodges-Simeon, C., Feingold, E., Marazita, M. L., Richmond, S., Shriver,
M. D., Claes, P., Shaffer, J. R., \& Weinberg, S. M. (2018). SNPs
associated with testosterone levels influence human facial morphology
{[}Journal Article{]}. \emph{Frontiers in Genetics}, \emph{9}(497).
\url{https://doi.org/10.3389/fgene.2018.00497}

\leavevmode\hypertarget{ref-Kelso_2017_BCCIP}{}%
Kelso, A. A., Goodson, S. D., Watts, L. E., Ledford, L. L., Waldvogel,
S. M., Diehl, J. N., Shah, S. B., Say, A. F., \textbf{White, Julie D.},
\& Sehorn, M. G. (2017). The β-isoform of bccip promotes adp release
from the rad51 presynaptic filament and enhances homologous dna pairing
{[}Journal Article{]}. \emph{Nucleic Acids Res}, \emph{45}(2), 711--725.
\url{https://doi.org/10.1093/nar/gkw877}

\endgroup

\hypertarget{non-peer-reviewed}{%
\subsection{Non peer-reviewed}\label{non-peer-reviewed}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_nonreviewed}{}
\leavevmode\hypertarget{ref-White__2019_Attractiveness}{}%
\textbf{White, Julie D.}, \& Puts, D. A. (2019). Genes influence facial
attractiveness through intricate biological relationships {[}Journal
Article{]}. \emph{PLOS Genetics}, \emph{15}(4), e1008030.
\url{https://doi.org/10.1371/journal.pgen.1008030}

\endgroup

\hypertarget{grants-and-awards}{%
\section{Grants and Awards}\label{grants-and-awards}}

\begin{cventries}
    \cventry{National Science Foundation DDRIG (\$31,535; awarded but declined)}{}{}{2019}{}\vspace{-4.0mm}
    \cventry{PSU Hill Fellowship Award (\$1500 and \$1200)}{}{}{2017-2018}{}\vspace{-4.0mm}
    \cventry{UW Summer Institutes in Statistical Genetics Travel Award (\$1800)}{}{}{2017}{}\vspace{-4.0mm}
    \cventry{PSU RGSO Conference Travel Award (\$400 each year)}{}{}{2016-2018}{}\vspace{-4.0mm}
    \cventry{PSU Center for Human Evolution and Diversity Research Grant (\$7303}{}{}{2015}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{invited-presentations}{%
\section{Invited Presentations}\label{invited-presentations}}

\begin{cventries}
    \cventry{203 GWAS signals reveal combinatorial effects on the genetic architecture of facial shape}{Center for Craniofacial and Dental Genetics; Advances in Human Facial Genetics Meeting}{Pittsburgh, PA, USA}{2019}{}\vspace{-4.0mm}
    \cventry{Detecting asymmetry in 3D facial scans}{KU Leuven; Medical Imaging Center}{Leuven, Belgium}{2018}{}\vspace{-4.0mm}
    \cventry{Exploring genotype to phenotype connections}{University of Pretoria; Genetics department}{Pretoria, South Africa}{2016}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{conference-participation}{%
\section{Conference Participation}\label{conference-participation}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\endgroup

\hypertarget{pedagogical-experience}{%
\section{Pedagogical Experience}\label{pedagogical-experience}}

\hypertarget{student-advising}{%
\subsection{Student Advising}\label{student-advising}}

\hypertarget{primary-instructor}{%
\subsection{Primary Instructor}\label{primary-instructor}}

\hypertarget{graduate-student-instructor}{%
\subsection{Graduate Student
Instructor}\label{graduate-student-instructor}}

\hypertarget{professional-development}{%
\section{Professional Development}\label{professional-development}}

\hypertarget{university-and-professional-service}{%
\section{University and Professional
Service}\label{university-and-professional-service}}

\hypertarget{ad-hoc-reviewer}{%
\subsection{Ad Hoc Reviewer}\label{ad-hoc-reviewer}}

\begin{itemize}
\tightlist
\item
  PLoS Genetics (1)
\item
  Scientific Reports (1)
\end{itemize}

\hypertarget{professional-memberships}{%
\section{Professional Memberships}\label{professional-memberships}}

\end{document}
